What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments

### 2024-06-08 manuscript.tex
Render Quarto Manuscript

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments},
  pdfauthor={Joshua R. de Leeuw1, Rachel Ryskin2, Ariel N. James3, Joshua K. Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A. Hwang1, Claire Iannetta1, Kristen M. Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
  pdflang={en-EN},
  pdfkeywords={eye-tracking, online, webcam, jsPsych, cognitive science},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{present-work}{%
\section{Present work}\label{present-work}}

@@

\hypertarget{selection-of-studies}{%
\subsection{Selection of Studies}\label{selection-of-studies}}

@@

\hypertarget{equipment}{%
\subsection{Equipment}\label{equipment}}

@@

\hypertarget{eye-tracking-calibration-and-validation}{%
\subsection{Eye-tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}}

@@

\hypertarget{data-pre-processing}{%
\subsection{Data pre-processing}\label{data-pre-processing}}

We used R (Version 4.2.1; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.2; Wickham, 2021a), \emph{ggplot2} (Version 3.4.0; Wickham, 2016), \emph{jsonlite} (Version 1.8.4; Ooms, 2014), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.5.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.1; Aust \& Barth, 2020), \emph{readr} (Version 2.1.3; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.3; Chang et al., 2021), \emph{stringr} (Version 1.5.0; Wickham, 2019), \emph{tidyr} (Version 1.3.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

\hypertarget{remote-sample}{%
\paragraph{Remote sample}\label{remote-sample}}

@@

\hypertarget{in-lab-sample}{%
\paragraph{In-lab sample}\label{in-lab-sample}}

@@

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

@@

@@

\hypertarget{materials-design}{%
\subsubsection{Materials \& Design}\label{materials-design}}

@@

\hypertarget{data-pre-processing-and-analysis}{%
\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{remote-sample-1}{%
\subsubsection{Remote sample}\label{remote-sample-1}}

\hypertarget{minimal-exclusion}{%
\paragraph{Minimal Exclusion}\label{minimal-exclusion}}

@@

\hypertarget{cumulative-fixation-probabilities}{%
\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}}

@@

\hypertarget{pre-noun-fixations}{%
\paragraph{Pre-noun fixations}\label{pre-noun-fixations}}

@@

\hypertarget{pre-verb-offset-fixations}{%
\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}}

@@

\hypertarget{first-target-fixations-after-verb}{%
\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}}

@@

\hypertarget{aggressive-exclusion}{%
\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}}

@@

\hypertarget{calibration}{%
\paragraph{Calibration}\label{calibration}}

@@

\hypertarget{in-lab-sample-1}{%
\subsubsection{In-lab sample}\label{in-lab-sample-1}}

\hypertarget{minimal-exclusion-1}{%
\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}}

@@

\hypertarget{cumulative-fixation-probabilities-1}{%
\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}}

@@

\hypertarget{pre-noun-fixations-1}{%
\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}}

@@

\hypertarget{pre-verb-offset-fixations-1}{%
\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}}

@@

\hypertarget{first-target-fixations-after-verb-1}{%
\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}}

@@

\hypertarget{calibration-1}{%
\paragraph{Calibration}\label{calibration-1}}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

@@

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

@@

\hypertarget{participants-2}{%
\subsubsection{Participants}\label{participants-2}}

@@

\hypertarget{procedure-1}{%
\subsubsection{Procedure}\label{procedure-1}}

@@

\begin{figure}
\includegraphics[width=5.47in]{group-b/E2-example-figure} \caption{Example trial from Experiment 2.}\label{fig:E2-example-trial}
\end{figure}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

\hypertarget{replication}{%
\subsubsection{Replication}\label{replication}}

@@

\hypertarget{calibration-2}{%
\subsubsection{Calibration}\label{calibration-2}}

@@

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

@@

\hypertarget{experiment-3}{%
\section{Experiment 3}\label{experiment-3}}

@@

\hypertarget{methods-2}{%
\subsection{Methods}\label{methods-2}}

@@

\hypertarget{participants-3}{%
\subsubsection{Participants}\label{participants-3}}

@@

\hypertarget{procedure-2}{%
\subsubsection{Procedure}\label{procedure-2}}

@@

\begin{figure}
\includegraphics[width=3.41in]{group-c/E3-example-figure} \caption{Schematic of the design of Experiment 3}\label{fig:E3-design-schematic}
\end{figure}

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

@@

\hypertarget{results-2}{%
\subsection{Results}\label{results-2}}

\hypertarget{day-1}{%
\paragraph{Day 1}\label{day-1}}

@@

\hypertarget{day-2}{%
\paragraph{Day 2}\label{day-2}}

@@

Participants correctly identified whether the image was familiar or unfamiliar 87.09\% (\emph{SD} = 10.49) of the time. After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = -9.36, p = 0.00 . Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = 3.43 , p = 0.00.

@@

\hypertarget{effects-of-rois}{%
\subsubsection{Effects of ROIs}\label{effects-of-rois}}

@@

\hypertarget{looking-scores}{%
\paragraph{Looking Scores}\label{looking-scores}}

@@

\hypertarget{correlations-with-day-2-performance}{%
\paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}}

@@

\hypertarget{calibration-3}{%
\subsubsection{Calibration}\label{calibration-3}}

\hypertarget{calibration-accuracy}{%
\paragraph{Calibration Accuracy}\label{calibration-accuracy}}

@@

\hypertarget{correlation-with-effects}{%
\paragraph{Correlation with Effects}\label{correlation-with-effects}}

@@

\hypertarget{discussion-2}{%
\subsection{Discussion}\label{discussion-2}}

@@

\hypertarget{experiment-4}{%
\section{Experiment 4}\label{experiment-4}}

@@

\hypertarget{methods-3}{%
\subsection{Methods}\label{methods-3}}

@@

\hypertarget{participants-4}{%
\subsubsection{Participants}\label{participants-4}}

@@

\hypertarget{procedure-3}{%
\subsubsection{Procedure}\label{procedure-3}}

@@

\begin{figure}
\includegraphics[width=4.5in]{group-d/E4-example-figure} \caption{An example of a critical trial from Experiment 4 for the sentence “Rub the butterfly with the crayon.” The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}\label{fig:E4-example-trial}
\end{figure}

\hypertarget{materials-1}{%
\subsubsection{Materials}\label{materials-1}}

@@

\hypertarget{results-3}{%
\subsection{Results}\label{results-3}}

\hypertarget{replication-1}{%
\subsubsection{Replication}\label{replication-1}}

@@

\hypertarget{comparison-to-in-lab-data}{%
\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}}

@@

\hypertarget{calibration-4}{%
\subsubsection{Calibration}\label{calibration-4}}

@@

\hypertarget{effects-of-rois-1}{%
\subsubsection{Effects of ROIs}\label{effects-of-rois-1}}

@@

\hypertarget{discussion-3}{%
\subsection{Discussion}\label{discussion-3}}

@@

\hypertarget{experiment-5}{%
\section{Experiment 5}\label{experiment-5}}

@@

\hypertarget{methods-4}{%
\subsection{Methods}\label{methods-4}}

@@

\hypertarget{participants-5}{%
\subsubsection{Participants}\label{participants-5}}

@@

\hypertarget{procedure-and-design}{%
\subsubsection{Procedure and Design}\label{procedure-and-design}}

@@

\begin{figure}
\includegraphics[width=3.41in]{group-e/E5-example-figure} \caption{An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}\label{fig:E5-example-trial}
\end{figure}

\hypertarget{materials-and-norming}{%
\subsubsection{Materials and Norming}\label{materials-and-norming}}

@@

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

@@

\hypertarget{results-4}{%
\subsection{Results}\label{results-4}}

@@

\hypertarget{calibration-5}{%
\subsubsection{Calibration}\label{calibration-5}}

@@

\hypertarget{effects-of-rois-2}{%
\subsubsection{Effects of ROIs}\label{effects-of-rois-2}}

@@

\hypertarget{discussion-4}{%
\subsection{Discussion}\label{discussion-4}}

@@

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altmannIncrementalInterpretationVerbs1999}{}}%
Altmann, G. T. M., \& Kamide, Y. (1999). Incremental interpretation at verbs: Restricting the domain of subsequent reference. \emph{Cognition}, \emph{73}(3), 247--264. \url{https://doi.org/10.1016/S0010-0277(99)00059-1}

\leavevmode\vadjust pre{\hypertarget{ref-anwyl2020gorilla}{}}%
Anwyl-Irvine, A. L., Massonnié, J., Flitton, A., Kirkham, N., \& Evershed, J. K. (2020). Gorilla in our midst: An online behavioral experiment builder. \emph{Behavior Research Methods}, \emph{52}, 388--407.

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-banki2022comparing}{}}%
Bánki, A., Eccher, M. de, Falschlehner, L., Hoehl, S., \& Markova, G. (2022). Comparing online webcam-and laboratory-based eye-tracking for the assessment of infants' audio-visual synchrony perception. \emph{Frontiers in Psychology}, \emph{12}, 733933.

\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}

\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using {lme4}. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}

\leavevmode\vadjust pre{\hypertarget{ref-R-broom.mixed}{}}%
Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}

\leavevmode\vadjust pre{\hypertarget{ref-R-shiny}{}}%
Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B. (2021). \emph{Shiny: Web application framework for r}. Retrieved from \url{https://CRAN.R-project.org/package=shiny}

\leavevmode\vadjust pre{\hypertarget{ref-deleeuwJsPsychJavaScriptLibrary2015}{}}%
de Leeuw, J. R. (2015). {jsPsych}: {A JavaScript} library for creating behavioral experiments in a {Web} browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12. \url{https://doi.org/10.3758/s13428-014-0458-y}

\leavevmode\vadjust pre{\hypertarget{ref-degen2021seeing}{}}%
Degen, J., Kursat, L., \& Leigh, D. D. (2021). Seeing is believing: Testing an explicit linking assumption for visual world eye-tracking in psycholinguistics. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{43}.

\leavevmode\vadjust pre{\hypertarget{ref-dijkgraaf2017predicting}{}}%
Dijkgraaf, A., Hartsuiker, R. J., \& Duyck, W. (2017). Predicting upcoming information in native-language and non-native-language auditory word recognition. \emph{Bilingualism: Language and Cognition}, \emph{20}(5), 917--930.

\leavevmode\vadjust pre{\hypertarget{ref-hayhoe2005eye}{}}%
Hayhoe, M., \& Ballard, D. (2005). Eye movements in natural behavior. \emph{Trends in Cognitive Sciences}, \emph{9}(4), 188--194.

\leavevmode\vadjust pre{\hypertarget{ref-henderson2017meaning}{}}%
Henderson, J. M., \& Hayes, T. R. (2017). Meaning-based guidance of attention in scenes as revealed by meaning maps. \emph{Nature Human Behaviour}, \emph{1}(10), 743--747.

\leavevmode\vadjust pre{\hypertarget{ref-henninger2021lab}{}}%
Henninger, F., Shevchenko, Y., Mertens, U. K., Kieslich, P. J., \& Hilbig, B. E. (2021). Lab. Js: A free, open, online study builder. \emph{Behavior Research Methods}, 1--18.

\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdest}{}}%
Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83.

\leavevmode\vadjust pre{\hypertarget{ref-james2023language}{}}%
James, A. N., Minnihan, C. J., \& Watson, D. G. (2023). Language experience predicts eye movements during online auditory comprehension. \emph{Journal of Cognition}, \emph{6}(1).

\leavevmode\vadjust pre{\hypertarget{ref-johanssonLookHereEye2014}{}}%
Johansson, R., \& Johansson, M. (2014). Look {Here}, {Eye Movements Play} a {Functional Role} in {Memory Retrieval}. \emph{Psychological Science}, \emph{25}(1), 236--242. \url{https://doi.org/10.1177/0956797613498260}

\leavevmode\vadjust pre{\hypertarget{ref-krajbich2010visual}{}}%
Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.

\leavevmode\vadjust pre{\hypertarget{ref-kukona2014lexical}{}}%
Kukona, A., Cho, P. W., Magnuson, J. S., \& Tabor, W. (2014). Lexical interference effects in sentence processing: Evidence from the visual world paradigm and self-organizing models. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 326.

\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

\leavevmode\vadjust pre{\hypertarget{ref-mannsVisualPairedcomparisonTask2000}{}}%
Manns, J. R., Stark, C. E. L., \& Squire, L. R. (2000). The visual paired-comparison task as a measure of declarative memory. \emph{Proceedings of the National Academy of Sciences}, \emph{97}(22), 12375--12379. \url{https://doi.org/10.1073/pnas.220398097}

>>>>

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments},
  pdfauthor={Joshua R. de Leeuw1, Rachel Ryskin2, Ariel N. James3, Joshua K. Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A. Hwang1, Claire Iannetta1, Kristen M. Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
  pdflang={en-EN},
  pdfkeywords={eye-tracking, online, webcam, jsPsych, cognitive science},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\section{Present work}\label{present-work}

@@

\subsection{Selection of Studies}\label{selection-of-studies}

@@

\subsection{Equipment}\label{equipment}

@@

\subsection{Eye-tracking Calibration and Validation}\label{eye-tracking-calibration-and-validation}

@@

\subsection{Data pre-processing}\label{data-pre-processing}

We used R (Version 4.4.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.3.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.5; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 1.0.0; Wickham, 2021a), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{jsonlite} (Version 1.8.8; Ooms, 2014), \emph{lme4} (Version 1.1.35.3; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.7.0; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{readr} (Version 2.1.5; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tidyr} (Version 1.3.1; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.4; Barth, 2022) for all our analyses.

\section{Experiment 1}\label{experiment-1}

@@

\subsection{Methods}\label{methods}

@@

\subsubsection{Participants}\label{participants-1}

\paragraph{Remote sample}\label{remote-sample}

@@

\paragraph{In-lab sample}\label{in-lab-sample}

@@

\subsubsection{Procedure}\label{procedure}

@@

\begin{verbatim}
## Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
## 3.5.0.
## i Please use the `legend.position.inside` argument of `theme()` instead.
## This warning is displayed once every 8 hours.
## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
## generated.
\end{verbatim}

@@

\subsubsection{Materials \& Design}\label{materials-design}

@@

\subsubsection{Data pre-processing and analysis}\label{data-pre-processing-and-analysis}

@@

\subsection{Results}\label{results}

\subsubsection{Remote sample}\label{remote-sample-1}

\paragraph{Minimal Exclusion}\label{minimal-exclusion}

@@

\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities}

@@

\paragraph{Pre-noun fixations}\label{pre-noun-fixations}

@@

\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations}

@@

\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb}

@@

\paragraph{Aggressive Exclusion}\label{aggressive-exclusion}

@@

\paragraph{Calibration}\label{calibration}

@@

\subsubsection{In-lab sample}\label{in-lab-sample-1}

\paragraph{Minimal Exclusion}\label{minimal-exclusion-1}

@@

\paragraph{Cumulative Fixation Probabilities}\label{cumulative-fixation-probabilities-1}

@@

\paragraph{Pre-noun fixations}\label{pre-noun-fixations-1}

@@

\paragraph{Pre-verb-offset fixations}\label{pre-verb-offset-fixations-1}

@@

\paragraph{First target fixations after verb}\label{first-target-fixations-after-verb-1}

@@

\paragraph{Calibration}\label{calibration-1}

@@

\subsection{Discussion}\label{discussion}

\section{Experiment 2}\label{experiment-2}

@@

\subsection{Methods}\label{methods-1}

@@

\subsubsection{Participants}\label{participants-2}

@@

\subsubsection{Procedure}\label{procedure-1}

@@

\begin{figure}
\centering
\includegraphics{group-b/E2-example-figure.jpeg}
\caption{\label{fig:E2-example-trial}Example trial from Experiment 2.}
\end{figure}

@@

\subsection{Results}\label{results-1}

\subsubsection{Replication}\label{replication}

@@

\subsubsection{Calibration}\label{calibration-2}

@@

\subsection{Discussion}\label{discussion-1}

@@

\section{Experiment 3}\label{experiment-3}

@@

\subsection{Methods}\label{methods-2}

@@

\subsubsection{Participants}\label{participants-3}

@@

\subsubsection{Procedure}\label{procedure-2}

@@

\begin{figure}
\centering
\includegraphics{group-c/E3-example-figure.jpeg}
\caption{\label{fig:E3-design-schematic}Schematic of the design of Experiment 3}
\end{figure}

\subsubsection{Materials}\label{materials}

@@

\subsection{Results}\label{results-2}

\paragraph{Day 1}\label{day-1}

@@

\paragraph{Day 2}\label{day-2}

@@

Participants correctly identified whether the image was familiar or unfamiliar 87.09\% (\emph{SD} = 10.49) of the time. After excluding the 3 participants who responded correctly to all images, the average confidence rating for correct responses (M = 3.51; SD = 0.41) was significantly higher than their average confidence ratings for incorrect responses (M = 2.55; SD = 0.75), t(44) = 9.36, p = 0.00 . Among the same subset of participants, response times for correct responses (M = 1,443.49, SD = 413.94) were also significantly faster than for incorrect responses (M = 2,212.65, SD = 1,733.76), t(44) = -3.43 , p = 0.00.

@@

\subsubsection{Effects of ROIs}\label{effects-of-rois}

@@

\paragraph{Looking Scores}\label{looking-scores}

@@

\paragraph{Correlations with Day 2 Performance}\label{correlations-with-day-2-performance}

@@

\subsubsection{Calibration}\label{calibration-3}

\paragraph{Calibration Accuracy}\label{calibration-accuracy}

@@

\paragraph{Correlation with Effects}\label{correlation-with-effects}

@@

\subsection{Discussion}\label{discussion-2}

@@

\section{Experiment 4}\label{experiment-4}

@@

\subsection{Methods}\label{methods-3}

@@

\subsubsection{Participants}\label{participants-4}

@@

\subsubsection{Procedure}\label{procedure-3}

@@

\begin{figure}
\centering
\includegraphics{group-d/E4-example-figure.jpeg}
\caption{\label{fig:E4-example-trial}An example of a critical trial from Experiment 4 for the sentence ``Rub the butterfly with the crayon.'' The butterfly is the target animal, the panda is the distractor animal, the crayon is the target instrument, and the violin is the distractor instrument.}
\end{figure}

\subsubsection{Materials}\label{materials-1}

@@

\subsection{Results}\label{results-3}

\subsubsection{Replication}\label{replication-1}

@@

\subsubsection{Comparison to in-lab data}\label{comparison-to-in-lab-data}

@@

\subsubsection{Calibration}\label{calibration-4}

@@

\subsubsection{Effects of ROIs}\label{effects-of-rois-1}

@@

\subsection{Discussion}\label{discussion-3}

@@

\section{Experiment 5}\label{experiment-5}

@@

\subsection{Methods}\label{methods-4}

@@

\subsubsection{Participants}\label{participants-5}

@@

\subsubsection{Procedure and Design}\label{procedure-and-design}

@@

\begin{figure}
\centering
\includegraphics{group-e/E5-example-figure.jpeg}
\caption{\label{fig:E5-example-trial}An example of a critical trial from Experiment 5. (Text did not appear on each screen.)}
\end{figure}

\subsubsection{Materials and Norming}\label{materials-and-norming}

@@

\subsubsection{Data analysis}\label{data-analysis}

@@

\subsection{Results}\label{results-4}

@@

\subsubsection{Calibration}\label{calibration-5}

@@

\subsubsection{Effects of ROIs}\label{effects-of-rois-2}

@@

\subsection{Discussion}\label{discussion-4}

@@

\section{General Discussion}\label{general-discussion}

@@

\section{References}\label{references}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-altmannIncrementalInterpretationVerbs1999}
Altmann, G. T. M., \& Kamide, Y. (1999). Incremental interpretation at verbs: Restricting the domain of subsequent reference. \emph{Cognition}, \emph{73}(3), 247--264. \url{https://doi.org/10.1016/S0010-0277(99)00059-1}

\bibitem[\citeproctext]{ref-anwyl2020gorilla}
Anwyl-Irvine, A. L., Massonnié, J., Flitton, A., Kirkham, N., \& Evershed, J. K. (2020). Gorilla in our midst: An online behavioral experiment builder. \emph{Behavior Research Methods}, \emph{52}, 388--407.

\bibitem[\citeproctext]{ref-R-papaja}
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\bibitem[\citeproctext]{ref-banki2022comparing}
Bánki, A., Eccher, M. de, Falschlehner, L., Hoehl, S., \& Markova, G. (2022). Comparing online webcam-and laboratory-based eye-tracking for the assessment of infants' audio-visual synchrony perception. \emph{Frontiers in Psychology}, \emph{12}, 733933.

\bibitem[\citeproctext]{ref-R-tinylabels}
Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}

\bibitem[\citeproctext]{ref-R-lme4}
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using {lme4}. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\bibitem[\citeproctext]{ref-R-Matrix}
Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}

\bibitem[\citeproctext]{ref-R-broom.mixed}
Bolker, B., \& Robinson, D. (2020). \emph{Broom.mixed: Tidying methods for mixed models}. Retrieved from \url{https://CRAN.R-project.org/package=broom.mixed}

\bibitem[\citeproctext]{ref-R-shiny}
Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B. (2021). \emph{Shiny: Web application framework for r}. Retrieved from \url{https://CRAN.R-project.org/package=shiny}

\bibitem[\citeproctext]{ref-deleeuwJsPsychJavaScriptLibrary2015}
de Leeuw, J. R. (2015). {jsPsych}: {A JavaScript} library for creating behavioral experiments in a {Web} browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12. \url{https://doi.org/10.3758/s13428-014-0458-y}

\bibitem[\citeproctext]{ref-degen2021seeing}
Degen, J., Kursat, L., \& Leigh, D. D. (2021). Seeing is believing: Testing an explicit linking assumption for visual world eye-tracking in psycholinguistics. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{43}.

\bibitem[\citeproctext]{ref-dijkgraaf2017predicting}
Dijkgraaf, A., Hartsuiker, R. J., \& Duyck, W. (2017). Predicting upcoming information in native-language and non-native-language auditory word recognition. \emph{Bilingualism: Language and Cognition}, \emph{20}(5), 917--930.

\bibitem[\citeproctext]{ref-hayhoe2005eye}
Hayhoe, M., \& Ballard, D. (2005). Eye movements in natural behavior. \emph{Trends in Cognitive Sciences}, \emph{9}(4), 188--194.

\bibitem[\citeproctext]{ref-henderson2017meaning}
Henderson, J. M., \& Hayes, T. R. (2017). Meaning-based guidance of attention in scenes as revealed by meaning maps. \emph{Nature Human Behaviour}, \emph{1}(10), 743--747.

\bibitem[\citeproctext]{ref-henninger2021lab}
Henninger, F., Shevchenko, Y., Mertens, U. K., Kieslich, P. J., \& Hilbig, B. E. (2021). Lab. Js: A free, open, online study builder. \emph{Behavior Research Methods}, 1--18.

\bibitem[\citeproctext]{ref-henrich2010weirdest}
Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--83.

\bibitem[\citeproctext]{ref-james2023language}
James, A. N., Minnihan, C. J., \& Watson, D. G. (2023). Language experience predicts eye movements during online auditory comprehension. \emph{Journal of Cognition}, \emph{6}(1).

\bibitem[\citeproctext]{ref-johanssonLookHereEye2014}
Johansson, R., \& Johansson, M. (2014). Look {Here}, {Eye Movements Play} a {Functional Role} in {Memory Retrieval}. \emph{Psychological Science}, \emph{25}(1), 236--242. \url{https://doi.org/10.1177/0956797613498260}

\bibitem[\citeproctext]{ref-krajbich2010visual}
Krajbich, I., Armel, C., \& Rangel, A. (2010). Visual fixations and the computation and comparison of value in simple choice. \emph{Nature Neuroscience}, \emph{13}(10), 1292--1298.

\bibitem[\citeproctext]{ref-kukona2014lexical}
Kukona, A., Cho, P. W., Magnuson, J. S., \& Tabor, W. (2014). Lexical interference effects in sentence processing: Evidence from the visual world paradigm and self-organizing models. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 326.

\bibitem[\citeproctext]{ref-R-lmerTest}
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

\bibitem[\citeproctext]{ref-mannsVisualPairedcomparisonTask2000}
Manns, J. R., Stark, C. E. L., \& Squire, L. R. (2000). The visual paired-comparison task as a measure of declarative memory. \emph{Proceedings of the National Academy of Sciences}, \emph{97}(22), 12375--12379. \url{https://doi.org/10.1073/pnas.220398097}

\bibitem[\citeproctext]{ref-R-jsonlite}
Ooms, J. (2014). The jsonlite package: A practical and consistent mapping between JSON data and r objects. \emph{arXiv:1403.2805 {[}Stat.CO{]}}. Retrieved from \url{https://arxiv.org/abs/1403.2805}

\bibitem[\citeproctext]{ref-papoutsaki2016webgazer}
Papoutsaki, A., Sangkloy, P., Laskey, J., Daskalova, N., Huang, J., \& Hays, J. (2016). {WebGazer}: {Scalable} webcam eye tracking using user interactions. \emph{Proceedings of the 25th International Joint Conference on Artificial Intelligence ({IJCAI})}, 3839--3845. {AAAI}.

\bibitem[\citeproctext]{ref-prystauka2023online}
Prystauka, Y., Altmann, G. T., \& Rothman, J. (2023). Online eye tracking and real-time sentence processing: On opportunities and efficacy for capturing psycholinguistic effects of different magnitudes and diversity. \emph{Behavior Research Methods}, 1--19.
